Generalized Bradley-Terry models

### 2025-03-06 inst/jss_hyper3_real.Rnw
typo

Here I analyse a dataset taken from recent e-sports tournament {\em
  ELEAGUE Major: Boston 2018}.  This Valve-sponsored Major featured 24
elite teams competing for a million dollar prize pool; peak concurrent
viewership exceeded $1.3\times 10^6$, the highest in CS:GO history at
the time.  I study the performance of tournament champions {\em
  Cloud9} who, as underdogs, narrowly defeated aggressive European
rivals {\em FaZe Clan} in the final.

>>>>

Here I analyse a dataset taken from recent e-sports tournament {\em
  ELEAGUE Major: Boston 2018}.  This Valve-sponsored Major featured 24
elite teams competing for a million dollar prize pool; peak concurrent
viewership exceeded $1.3\times 10^6$, the highest in {\em CS:GO}
history at the time.  I study the performance of tournament champions
{\em Cloud9} who, as underdogs, narrowly defeated aggressive European
rivals {\em FaZe Clan} in the final.
